---
title: "p8105_hw1_yy2912.Rmd"
output: github_document
---
##problem 1 create a dataframe with different variable types##

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

```{r}
q1dataframe = tibble(
  vec_numeric = rnorm(8),
  vec_logical = vec_numeric > 0,
  vec_char = c("This", "dataset", "comes", "from", "groups", "of", "cancer", "patients"),
  vec_factor = factor(c("young", "young", "young", "middleage","middleage","middleage", "old", "old"))
)

class(pull(q1dataframe, vec_numeric))
class(pull(q1dataframe, vec_logical))
class(pull(q1dataframe, vec_char))
class(pull(q1dataframe, vec_factor))

mean_numeric = mean(pull(q1dataframe, vec_numeric))
mean_logical = mean(pull(q1dataframe, vec_logical))
mean_char = mean(pull(q1dataframe, vec_char))
mean_factor = mean(pull(q1dataframe, vec_factor))
```
##when take mean of the variables, character and factor variables do not work; numeric and logical variable work ##

```{r}
set.seed(13)
x = as.numeric(q1dataframe$vec_logical)
y = as.numeric(q1dataframe$vec_char)
z = as.numeric(q1dataframe$vec_factor)

x*q1dataframe$vec_numeric
y*q1dataframe$vec_numeric
z*q1dataframe$vec_numeric
```
logical and factor variables can be converted to numeric variables but character variables cannot. This can explain why character variable cannot take the mean but cannot explain why factor variables cannot take the mean. 

##question 2 creates a dataframe 

```{r}
set.seed(13)

q2dataframe = tibble(
  x = rnorm(500, mean=0, sd=1),
  y = rnorm(500, mean=0, sd=1),
  vec_logical1 = x+y > 1,
  vec_numeric1 = as.numeric(vec_logical1),
  vec_factor1 = as.factor(vec_logical1), 
)

ggplot(q2dataframe, aes(x = x, y = y, color = vec_logical1)) + geom_point()

ggplot(q2dataframe, aes(x = x, y = y, color = vec_numeric1)) + geom_point()
       
ggplot(q2dataframe, aes(x = x, y = y, color = vec_factor1)) + geom_point()
```
##save the first scatterplot using ggsave
```{r}  
ggsave("hw1_yy2912.pdf")
```

##the number of rows in the dataset is `r nrow(q2dataframe)` and the number of column in the dataset is `r ncol(q2dataframe)`

## the mean is `r mean(pull(q2dataframe, x))`, 
the median is `r median(pull(q2dataframe, x))`, 
and standard deviation is `r sd(pull(q2dataframe, x))` 
the proportion of cases for which x + y > 1 is `r length(q2dataframe$vec_logical1)`

